\documentclass[twocolumn]{article}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{kpfonts}[maths]
\usepackage{libertine}
\usepackage{placeins}
\usepackage{gensymb}
\usepackage{inconsolata}
\usepackage{subcaption}
\usepackage{mdframed}
\usepackage{caption}
\usepackage{amsmath}
\usepackage{lipsum}
\usepackage{tikz}
\usepackage{minted}
\usepackage{lipsum}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{biblatex}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    citecolor=black,
}

\definecolor{CERNblue}{HTML}{22529e}
\definecolor{CodeBg}{rgb}{0.95, 0.95, 0.95}

\setminted{
    % linenos=true,
    autogobble=true,
    frame=single,
    % framesep=2mm,
    % framerule=0.4pt,
    tabsize=4,
    fontsize=\footnotesize,
    breaklines,
    bgcolor=CodeBg,
}

\setlist[enumerate]{itemsep=0mm}
\setlist[itemize]{itemsep=-0mm}


\sectionfont{\color{CERNblue}}
\subsectionfont{\color{CERNblue}}

\newcommand{\hypermail}[1]{\href{mailto:#1}{\texttt{<#1>}}}

% TODO: change footnote style

% TODO: add a link to the repository somewhere

\title{D/E7039E --- Project in Industrial Computer Systems/Electronical Systems \& Control Technology}
\author{
As authored by:
\footnote{In no particular order.}
\footnote{All team members can be contacted via
\href{mailto:vikson-6@student.ltu.se;lukkar-4@student.ltu.se;simpen-1@student.ltu.se;olemis-6@student.ltu.se;rubasp-6@student.ltu.se;alinou-6@student.ltu.se;alikhar-6@student.ltu.se}{this hyperlink}.} \\
Viktor Sonesten \hypermail{vikson-6@student.ltu.se} \\
Lukas Karlsson \hypermail{lukkar-4@student.ltu.se} \\
Simon Sandberg \hypermail{simpen-1@student.ltu.se} \\
Oleksiy Mishchenko \hypermail{olemis-6@student.ltu.se} \\
Ruben Asplund \hypermail{rubasp-6@student.ltu.se} \\
Ali Nouri \hypermail{alinou-6@student.ltu.se} \\
Ali Khademi \hypermail{alikha-6@student.ltu.se}
}
\date{\today}

\begin{document}
\maketitle

\appendix
\section{Team Members}
The team's members are below listed along with their preliminary areas of concern throughout the development of this project.

\begin{description}
    \item[Viktor Sonesten]
    Any embedded programming;
    repository maintainership; and
    report typesetting.

    \item[Lukas Karlsson]
    Embedded programming and
    Computer vision/position control.
    \item[Simon Sandberg]
    Position and grip control.
    Sensor data integration and tuning.
    Embedded programming.
    \item[Oleksiy Mishchenko]
    Sensor implementation and tuning;
    Implementation and tuning of control systems;
    Embedded programming;
    \item[Ruben Asplund]
    Arrowhead and embedded programming.
    \item[Ali Nouri]
    Embedded programming;
    Invers kinematics modeling;
    Choose/design a navigation system;
    \item[Ali Khademi]
\end{description}

\section{Preliminary Way of Work}
All members will meet each workday in the lab at 9 AM if able to work on the project.

Every Monday after lunch a meeting will be held to wrap up the previous week and make any necessary preparations for the Tuesday presentation.

After each day it is recommended to write down what sub-projects one has worked on and what is planned for the next day/week;
this will greatly streamline the Monday meetings and ensure that every team member always have something to work on.

If we later find a better way to manage our work,
or if we find that we deviate from what is planned above,
an updated Way of Work will be appended to the appendix of this document.

\end{document}
